Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-07-02 analysis/paper/paper.Rmd
Further edits for grammar corrections

There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
Assuming that a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
Here we define three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.

@@

Ideally, once the data are complete, best practices for keeping your data as you perform your work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
It should be noted that the use of a database management system also allows for both of these at the expense of added complexity.
Saving files in proprietary formats such as .xls(x) can also lead to issues in the future when opening using newer (or older) software versions.
Unexpected changes to values in the data [@Ziemann2016] may also occur when using proprietary formats.

>>>>

There are different ways to make research more open and reproducible, which can be thought of as levels of reproducibility.
If a general workflow for producing academic research involves clearly defining a research question, obtaining data for testing the hypothesis, summarizing/analyzing and presenting data and results, writing the manuscript then the next logical steps are depositing the code used along with the raw data in proper repositories (Figure \@ref(fig:workflow-dia)).
Here we define three levels of reproducibility which are also related to the evolution of computational methods and reproducible practices and highlight papers that fit these definitions.

@@

Ideally, once the data are complete, best practices for keeping your data as you perform your work include treating the raw data as read-only and using file permissions to prevent changes to the raw data files.
It should be noted that the use of a database management system also allows for both at the expense of added complexity.
Saving files in proprietary formats such as .xls(x) can also lead to issues in the future when opening using newer (or older) software versions.
Unexpected changes to values in the data [@Ziemann2016] may also occur when using proprietary formats.
